### 2017-04-07 paper/intro.tex
pass on intro

The dimensions of analysis we considered in this study are as follows:
potential, effectiveness, adoption, and tradeoffs.  Each dimension
focuses on one aspect of our study.  The dimension \textbf{potential}
measures the potential of parallelization to reduce testing costs.  In
the limit, parallelization would be fruitless if all projects used
short-running test suites or if the bulk of execution cost was
dominated by a single test in the suite.  The dimension
\textbf{effectiveness} measures the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} on testing costs.  Intuitively, benefits are
proportional to the cost reduction that parallelization brings.  In
the limit, the overhead of spawning virtual machines or threads can
even result in added cost.  The dimension \textbf{adoption} evaluates
(i) how often open-source projects use parallelization schemes and
(ii) how developers involved in costly projects (not using test suite
parallelization) perceive this technology.  It is important to measure
resistance to the technology and its reasons.  Finally, the dimension
\textbf{tradeoffs} evaluates the issues and benefits associated
with\Comment{running test suites with} different parallel
configurations.  Note that the configuration choice can affect both
test cost and test flakiness, which is caused by the non-determinism
resulted from running test methods and classes in different
orderings.

@@

\Mar{organize according to each of these dimensions...$\rightarrow$}

@@

%% RQ1 + RQ2
We selected \numSubjs{} popular Java projects from \github{}
containing Maven build files~\cite{maven} to assess how prevalent
long-running test suites are.  Section~\ref{sec:eval} details our
methodology to select subjects and to isolate our experiments from
environmental noise.  In summary, results indicate that $\sim$21\% of
the test suites take at least 1m to run and $\sim$8\% of the test
suites take at least 5m to run.  Considering all the \numMedLong{}
projects in the $>$1m group (\percentMedLongRunning{} of
\numSubjs{})\Fix{$\leftarrow$this is not right. check macros.}, the
average execution time is \averageMedLongRunning{}.  Results also show
that individual tests are typically short-running, taking often less
than half a second to run.  Furthermore, we found that only in rare
cases few test cases monopolize execution cost associated with each
test suite.  Overall, these results suggest that test suite
parallelization has the potential to optimize these test suites.

%%RQ3
Given the high execution cost associated with a significant number of
\github{} projects, we decided to investigate usage of test
suite parallelization in practice.  It is important to note that modern build
systems (\eg{}, Maven~\cite{maven}) offer parallelization options to
accelerate test execution (see Section~\ref{sec:modes}).  To find how
popular these features are in practice, we first analyzed build files
\emph{statically}.  Considering the $>$1m group of projects
(\numMedLong{} in total), we found that 49\% (41/\numMedLong{}) of
them use some parallelization option.  Considering those projects that
take more than 5m to run (\numLong{} in total), usage of parallelism
increases to 59\% (19/\numLong{}).  Furthermore, we found that
``forking'' virtual machines was the most prevalent parallel mode used
in practice.  This mode is used twice as much as any other mode used.
Important to note that ``forking VMs'' is perhaps the simplest of the
parallelization modes~--~it is provided by the build system as opposed
to the testing framework.  This result suggests that datarace
flakiness~\cite{luo-etal-fse2014} may be a concern to users as
``forking'' does not exploit thread-level concurrency within each VM,
which can create contention on data reachable from the static
area~\cite{bell-kaiser-icse2014,bell-etal-esecfse2015}.  Instead, it
creates independent processes (\ie{}, Java VM instances) and executes
tests sequentially within each process. \Mar{why 32-19 did not use
  parallelization?}

\Fix{...Discuss impact...}\Mar{what about free services (jenkins)?
  how much can you scale execution and how expensive would that be?}

>>>>

The dimensions of analysis we considered in this study are as follows:
potential, effectiveness, adoption, and tradeoffs.  Each dimension
focuses on one aspect of our study.  The dimension \textbf{potential}
measures the potential of parallelization to reduce testing costs.  In
the limit, parallelization would be fruitless if all projects used
short-running test suites or if the bulk of execution cost was
dominated by a single test in the suite.  The dimension
\textbf{effectiveness} measures the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} on testing costs.  Intuitively, benefits are
proportional to the cost reduction that parallelization brings.  In
the limit, however, the overhead of spawning virtual machines or
threads can even result in added cost.  The dimension
\textbf{adoption} evaluates (i) how often open-source projects use
parallelization schemes and (ii) how developers involved in costly
projects (not using test suite parallelization) perceive this
technology.  It is important to measure resistance to the technology
and its reasons.  Finally, the dimension \textbf{tradeoffs} evaluates
the issues and benefits associated with\Comment{running test suites
  with} different parallel configurations.  Note that the
configuration choice can affect both test cost and test flakiness,
which is caused by the non-determinism resulted from running test
methods and classes in different orderings.

@@

@@

\subsection{Summary of ``Potential'' results}

We selected \numSubjs{} popular Java projects from \github{}
containing Maven build files~\cite{maven} to assess how prevalent
long-running test suites are.  Section~\ref{sec:eval} details our
methodology to select subjects and to isolate our experiments from
environmental noise.  Results indicate that nearly
\percentMedLongRunning{} of the projects take at least 1m to run their
test suites and \percentLongRunning{} of the projects take at least 5m
to run their suites.  Considering the \numMedLong{} projects in those
two groups, the average execution time is \averageMedLongRunning{}.
Results also show that individual tests are typically short-running,
taking often less than half a second to run.  Furthermore, we found
that only in rare cases few test cases monopolize execution cost
associated with each test suite.  \emph{Overall, our results suggest
  that test suite parallelization has the potential to optimize test
  suites.}

\subsection{Summary of ``Effectiveness'' results}

As to avoid introduction of unintended noise when measuring time, we
evaluated effectiveness on projects that we knew a priori ran their
test suite in parallel by default.  Results indicate that the average
speedup of parallelization was \avgSpeedup{}x.  Although we found
cases with very high speedups (\eg{}, 9.2x), we found some cases where
speedups were insignificant.  \emph{Overall, our results suggest that
  it may not be obvious to achieve huge speedups with test suite
  parallelization.}

\subsection{Summary of ``Adoption'' results}

We considered two aspects in measuring adoption of the technology.
First, we analyzed quantitatively current usage of parallelism in
open-source projects.  Then, we investigated the key reasons that
justify resistance of developers in using test suite parallelization.
For the quantitative analysis we checked both statically (parsing
build files) and dynamically (monitoring execution of build files) for
the presence of parallelization.  Considering only those projects that
take longer than a minute to run their test suites, we found that only
\percentParallel{} of them use parallelism.  When considering the
feedback received from developers involved in those projects we
realized the proportion should was a bit higher, of
\percentParallelUpdated{}, but still relatively low.  For the
qualitative analysis we surveyed developers from a selection of costly
projects that did not use parallelization.  Section~\ref{sec:rqE}
details our selection methodology. \emph{Results indicate that dealing
  with concurrency issues related with parallelization (in particular,
  the extra work to organize test suite to safely explore concurrency)
  was the main barrier for adoption.  Other reasons included
  availability of continuous integration services and unfamiliarity
  with the technology.}

%% %%RQ3
%% Given the high execution cost associated with a significant number of
%% \github{} projects, we decided to investigate usage of test
%% suite parallelization in practice.  It is important to note that modern build
%% systems (\eg{}, Maven~\cite{maven}) offer parallelization options to
%% accelerate test execution (see Section~\ref{sec:modes}).  To find how
%% popular these features are in practice, we first analyzed build files
%% \emph{statically}.  Considering the $>$1m group of projects
%% (\numMedLong{} in total), we found that 49\% (41/\numMedLong{}) of
%% them use some parallelization option.  Considering those projects that
%% take more than 5m to run (\numLong{} in total), usage of parallelism
%% increases to 59\% (19/\numLong{}).  Furthermore, we found that
%% ``forking'' virtual machines was the most prevalent parallel mode used
%% in practice.  This mode is used twice as much as any other mode used.
%% Important to note that ``forking VMs'' is perhaps the simplest of the
%% parallelization modes~--~it is provided by the build system as opposed
%% to the testing framework.  This result suggests that datarace
%% flakiness~\cite{luo-etal-fse2014} may be a concern to users as
%% ``forking'' does not exploit thread-level concurrency within each VM,
%% which can create contention on data reachable from the static
%% area~\cite{bell-kaiser-icse2014,bell-etal-esecfse2015}.  Instead, it
%% creates independent processes (\ie{}, Java VM instances) and executes
%% tests sequentially within each process. \Mar{why 32-19 did not use
%%   parallelization?}

\subsection{Summary of ``Tradeoff'' results}

\Fix{bla bla bla bla bla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla bla}
